---
title: "Plots created for CDS 2026 poster"
format:
  html:
    toc: true
---
```{r echo=FALSE}
library(tidyverse)
library(here)
library(reticulate)
library(dotenv)
library(readr)
library(gghalves)
#devtools::install_github("langcog/wordbankr")
library(ggrepel)
library(relayer) # devtools::install_github("clauswilke/relayer")
library(viridis)
library(RColorBrewer)
library(lmerTest)
library(cowplot)
library(ggtext)
library(scales)
source(here("analysis/helpers.R"))

env_file = here(".env")
default_project = "main"
if (file.exists(env_file)) {
  load_dot_env(file = env_file)
  PROJECT_VERSION <- Sys.getenv("PROJECT_VERSION")
  if (PROJECT_VERSION == "") {
    PROJECT_VERSION <- default_project
  }
} else {
  PROJECT_VERSION <- default_project
}
```

```{r}
PROCESSED_DATA_PATH = here("data","main","processed_data")
trial_summary_data <- read.csv(here(PROCESSED_DATA_PATH, "level-trials_data.csv"))
trial_metadata <- read.csv(here("data", "metadata", "level-trialtype_data.csv"))
all_similarities <- read.csv(here("data", "embeddings", "similarities-all_data.csv"))
target_looking_trial_level <- read.csv(here("data", PROJECT_VERSION, "processed_data", "level-trials_data.csv"))
looking_data_summarized <- trial_summary_data |>
  filter(trial_exclusion == 0 & exclude_participant == 0 & exclude_participant_insufficient_data == 0) |>
  left_join(trial_metadata) |>
  arrange(AoA_Est_target)
```

```{r}
sim_data <- trial_metadata |> left_join(all_similarities, by=c("Trials.targetImage"="text1", "Trials.distractorImage"="text2")) |> distinct(clip_multimodal_similarity, .keep_all=TRUE)
sim_data <- sim_data |>
  mutate(
    fitted = predict(lm(image_similarity ~ dinov3.babyview_image_similarity, data = sim_data)),
    residual = abs(image_similarity - fitted),
    is_outlier = residual > (mean(residual) + 0.2*sd(residual))
  ) 

clip_bv <- ggplot(sim_data, aes(x=dinov3.babyview_image_similarity, y=image_similarity)) +
  geom_smooth(method="lm", color="#215D89", alpha=0.5, se=FALSE) +
  geom_smooth(method="lm", color="#215D89", se=TRUE, alpha=0.2) +
  geom_point(size=8, alpha=0.8, color="#215D89") +
  scale_y_continuous(breaks = seq(0.4, 0.8, by = 0.2)) +
  geom_label_repel(
    data = sim_data |> filter(is_outlier),
    aes(label=Trials.imagePair),
    color="black",
    fill="white",
    alpha=0.8,
    segment.alpha=0.7,
    nudge_y=0.02,
    force=10,
    force_pull=0.1,
    segment.size=1.2,
    size=6
  ) +
  ylab("CLIP image similarity") +
  xlab("BabyView model similarity") +
  theme_classic() +
  theme(
    text = element_text(size=14, face="bold"),
    axis.title.x = element_text(face="bold", size=20, margin=margin(t=15, r=0, b=0, l=0)),
    axis.title.y = element_text(face="bold", size=20, margin=margin(t=0, r=10, b=0, l=0)),
    axis.text = element_text(size=16, face="bold"),
    legend.key = element_blank(),
    legend.title = element_text(size=22, face="bold"),
    legend.text = element_text(size=22, face="bold"),
    legend.position = "bottom",
    panel.spacing = unit(0.5, "cm")
  )
ggsave(here("figures","cds","clip_bv.svg"),clip_bv,width=6.67, height=3.2,units="in", bg = "white",device="pdf")

dino_bv <- ggplot(sim_data, aes(x=dinov3.babyview_image_similarity, y=image_similarity)) +
  geom_point(size=3, color = "#215D89") +
  geom_smooth(method="lm", color = "#215D89") +
  geom_label_repel(aes(label=Trials.imagePair),size = 6) +
  ylab("CLIP Image Similarity") +
  xlab("DINO-BabyView Similarity") +
  theme(text = element_text(size=18)) +
  theme_classic() 
```

# helpers
```{r}
fit_image_model <- function(summary_data) {
  lmer(
    scale(corrected_target_looking) ~ 
      scale(image_similarity) * scale(age_in_months) + 
      scale(AoA_Est_target) + 
      scale(MeanSaliencyDiff) +
      (1 | SubjectInfo.subjID) +
      (1 | Trials.targetImage),
    data = summary_data |> 
      mutate(age_in_months = SubjectInfo.testAge / 30)
  )
}

fit_text_model <- function(summary_data) {
  lmer(
    scale(corrected_target_looking) ~ 
      scale(text_similarity) * scale(age_in_months) + 
      scale(AoA_Est_target) + 
      scale(MeanSaliencyDiff) +
      (1 | SubjectInfo.subjID) +
      (1 | Trials.targetImage),
    data = summary_data |> 
      mutate(age_in_months = SubjectInfo.testAge / 30)
  )
}
```

# CLIP plot
```{r}
multiple_similarity_effects_plot <- function(data, x_var, y_var="mean_value", group_var, input_title, prod = FALSE) {
  sim_type <- strsplit(x_var, "_")[[1]][1]
  
  # Conditionally filter data if prod is TRUE
  if (prod) {
    label_data <- data %>% 
      filter(Trials.targetImage == "acorn" | Trials.distractorImage == "acorn") %>%
      mutate(label = paste("Target:", Trials.targetImage, "\nDistractor:", Trials.distractorImage))
  } else {
    label_data <- data %>%
      mutate(label = paste("Target:", Trials.targetImage, "\nDistractor:", Trials.distractorImage))
  }
  
  # Create base plot
  p <- ggplot(data, aes(x = .data[[x_var]], y = .data[[y_var]])) +  # Removed color from aes()
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_point(size = 8, alpha = 0.5, color = "#215D89") +  # Set color outside aes()
    geom_smooth(alpha = 0.3, size = 0, method = "lm", show.legend = F, color = "#215D89") +  # Set color outside aes()
    stat_smooth(geom = "line", alpha = 0.9, size = 1.5, method = "lm", show.legend = F, color = "#215D89") +  # Set color outside aes()
    coord_cartesian(ylim = c(-0.12, 0.22)) +
    geom_label_repel(
      data = label_data,
      aes(label = label),
      segment.alpha = 0.7,
      nudge_y = ifelse(label_data$Trials.targetImage == "bulldozer", -0.02, 0.02),
      force = 10,
      force_pull = 0.1,
      size = 4,
      segment.size = 1.2,
      point.padding = unit(1, "lines"),
      min.segment.length = 0,
      box.padding = unit(0.5, "lines"),
      max.overlaps = Inf,
      label.padding = unit(0.25, "lines"),
      label.r = unit(0.5, "lines"),
      show.legend = FALSE
    )+
    ylab("Baseline-corrected\nproportion target looking") +
    xlab("Target-distractor embedding similarity") +
    scale_y_continuous(breaks = seq(-0.1, 0.2, by = 0.1)) +
    theme_minimal()+
    theme(
      text = element_text(size = 16, face = "bold"),
      axis.title.x = element_text(
        face = "bold", 
        size = 29,
        margin = margin(t = 15, r = 0, b = 0, l = 0)
      ),
      legend.key = element_blank(),
      axis.title.y = element_text(
        face = "bold", 
        size = 29,
        margin = margin(t = 0, r = 10, b = 0, l = 0)
      ),
      axis.text = element_text(size = 24, face = "bold"),
      legend.title = element_text(size = 22, face = "bold"),
      legend.text = element_text(size = 22, face = "bold"),
      legend.position = "bottom",
      strip.text = element_text(size = 28, face = "bold"),
      strip.background = element_rect(fill = "gray90", color = NA),
      strip.text.x = element_text(margin = margin(t = 8, b = 8)), # Increase padding within strip
      panel.spacing = unit(0.5, "cm")
    ) +
   facet_wrap(facets=~ .data[[group_var]],dir="v", strip.position="top", labeller = as_labeller(c("image_similarity" = "Image Similarity", "text_similarity" = "Text Similarity")),
              ncol=1, scales = "free")
  
  # Conditionally add facetted_pos_scales if prod is TRUE
  if (prod) {
    p <- p + facetted_pos_scales(
      x = list(
        image_similarity = scale_x_continuous(
          breaks = seq(0.4, 0.9, by = 0.1),
          limits = c(0.38, 0.9)
        ),
        text_similarity = scale_x_continuous(
          breaks = seq(0.65, 0.9, by = 0.05),
          limits = c(0.62, 0.93)
        )
      )
    )
  }
  
  return(p)
}
```

```{r}
clip_data_summarized <- summarize_similarity_data(looking_data_summarized)
clip_data_long <- clip_data_summarized |>
  pivot_longer(cols = c("text_similarity", "image_similarity"), names_to = "sim_type", values_to = "similarity")
all_clip_plot <- multiple_similarity_effects_plot(clip_data_long, "similarity", group_var="sim_type", input_title="Looking time and CLIP embedding correlations", prod=TRUE)
all_clip_plot
ggsave(here("figures",PROJECT_VERSION,"clip_plot_poster.png"),all_clip_plot,width=7.5, height=10,bg = "white",device="pdf")
```

```{r}
image_similarity_effects_plot <- function(
    data,
    x_var = "image_similarity",
    y_var = "mean_value",
    input_title = NULL
) {
  
  label_data <- data %>% 
    filter(
      Trials.targetImage == "acorn" |
        Trials.distractorImage == "acorn"
    ) %>%
    mutate(
      label = paste(
        "Target:", Trials.targetImage,
        "\nDistractor:", Trials.distractorImage
      )
    )
  
  ggplot(data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_point(size = 8, alpha = 0.5, color = "#215D89") +
    geom_smooth(
      alpha = 0.3, size = 0,
      method = "lm", show.legend = FALSE,
      color = "#215D89"
    ) +
    stat_smooth(
      geom = "line", alpha = 0.9,
      size = 1.5, method = "lm",
      show.legend = FALSE,
      color = "#215D89"
    ) +
    coord_cartesian(ylim = c(-0.12, 0.22)) +
    geom_label_repel(
      data = label_data,
      aes(label = label),
      segment.alpha = 0.7,
      nudge_y = ifelse(
        label_data$Trials.targetImage == "acorn",
        -0.02, 0.02
      ),
      force = 10,
      force_pull = 0.1,
      size = 8,
      segment.size = 1,
      point.padding = unit(1, "lines"),
      min.segment.length = 0,
      box.padding = unit(0.5, "lines"),
      max.overlaps = Inf,
      label.padding = unit(0.25, "lines"),
      label.r = unit(0.5, "lines"),
      show.legend = FALSE
    ) +
    ylab("Baseline-corrected\nproportion target looking") +
    xlab("Target-distractor high-level visual similarity") +
    scale_y_continuous(breaks = seq(-0.1, 0.2, by = 0.1)) +
    scale_x_continuous(
      breaks = seq(0.5, 0.9, by = 0.1),
      limits = c(0.43, 0.85)
    ) +
    theme_classic() +
    theme(
      text = element_text(size = 16, face = "bold"),
      axis.title.x = element_text(
        size = 20, face = "bold",
        margin = margin(t = 15)
      ),
      axis.title.y = element_text(
        size = 20, face = "bold",
        margin = margin(r = 10)
      ),
      axis.text = element_text(size = 18, face = "bold")
    )
}
image_clip_plot <- image_similarity_effects_plot(clip_data_summarized)
image_clip_plot
ggsave("image_clip_plot.svg", height=8, width=7, device="pdf")
```
# AoA plot
```{r, fig.width=6.936, fig.height=9.437, fig.units="in"}
target_looking_item_subject_level <- summarized_data(looking_data_summarized, "Trials.targetImage", "corrected_target_looking", c("SubjectInfo.subjID", "SubjectInfo.testAge", "AoA_Est_target", "section"))

target_looking_item_level <- summarized_data(target_looking_item_subject_level |> rename(mean_target_looking = mean_value), "Trials.targetImage", "mean_target_looking", c("AoA_Est_target", "section"))

aoa_jittered <- target_looking_item_level %>%
  rowwise() %>%
  mutate(aoa_x_jittered = AoA_Est_target + runif(n(), -0.01, 0.01))

aoa_across_time <- ggplot(aoa_jittered, aes(x=aoa_x_jittered, y=mean_value))+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=8, color="#E95454", alpha=0.6)+ #, aes(alpha=section)
  scale_alpha_manual(values = c(sample1 = 0.8, sample2 = 0.3)) +
  #geom_linerange(aes(ymin = mean_value - ci, ymax = mean_value + ci), alpha = 0.1) + 
  geom_smooth(method="lm", color="#E95454", alpha=0.5, se=FALSE) +
geom_smooth(method="lm", color="#E95454", se=TRUE, alpha=0.2) +
  geom_label_repel(data=aoa_jittered |> filter(AoA_Est_target > 5.7 | (AoA_Est_target < 5 & AoA_Est_target > 4.5) | Trials.targetImage %in% c("airplane", "mud", "worm", "car", "butterfly", "duck", "acorn", "coconut", "key", "truck") | (mean_value > 0.1 & AoA_Est_target > 4)), size=7,aes(label=Trials.targetImage),force_pull=15,nudge_y=-0.03) +
  xlab("Estimated target word age-of-acquisition (AoA)")+
  ylab("Baseline-corrected\nproportion target looking")+
  #ggtitle("Prop. of target looking by estimated AoA of target words")+
  theme_classic()+
  guides(shape = "none", alpha="none") +
 theme(
    text = element_text(size=10,face = "bold"),              # All text bold
    # Increase space between x-axis and its title
    axis.title.x = element_text(
      face = "bold", 
      size = 24,
      margin = margin(t = 10, r = 0, b = 0, l = 0)
    ),
    
    # Increase space between y-axis and its title
    axis.title.y = element_text(
      face = "bold", 
      size= 24,
      margin = margin(t = 10, r = 5, b = 0, l = 0)
    ),      
    axis.text = element_text(size=20),         # Axis text bold
    #legend.title = element_text(size = 12, face = "bold"),  # Small bold legend title
    #legend.text = element_text(size = 12, face = "bold")    # Small bold legend text
  )+
 scale_x_continuous(breaks = seq(3, 6, by = 0.5)) +
   coord_cartesian(xlim = c(3.2,6.5), ylim = c(-0.16, 0.18))
aoa_across_time
ggsave(here("figures","cds","aoa_plot_alpha.svg"),aoa_across_time,height=6.936,width=9.437,units="in",bg = "white", device="pdf")
```
# DINO plots
```{r}
multiple_similarity_effects_plot_refactored <- function(
    data, 
    x_var, 
    y_var = "mean_value", 
    group_var, 
    input_title,
    label_filter = NULL,       # quoted expr string, e.g. "Trials.targetImage == 'acorn'"
    nudge_target_col = NULL,   # column name to base nudge_y on
    nudge_target_val = NULL,   # value in that column that gets nudge down
    facet_labels = NULL,       # named vector for labeller, NULL = use values as-is
    facet_scales_x = NULL,     # named list of scale_x_continuous() per facet level
    ylim = c(-0.12, 0.22),
    color = "#215D89",
     color_map = NULL,       # named vector, e.g. c("Text Similarity" = "#C76D48"),
    facet_dir = "h",
    n_col = 3
) {
  
  # Label data
  if (!is.null(label_filter)) {
    label_data <- data %>% filter(eval(parse(text = label_filter)))
  } else {
    label_data <- data
  }
  label_data <- label_data %>%
    mutate(label = paste("Target:", Trials.targetImage, "\nDistractor:", Trials.distractorImage))
  
  # nudge_y
  if (!is.null(nudge_target_col) && !is.null(nudge_target_val)) {
    nudge_vals <- ifelse(label_data[[nudge_target_col]] == nudge_target_val, -0.02, 0.02)
  } else {
    nudge_vals <- 0.02
  }
  
  # Labeller
  labeller_fn <- if (!is.null(facet_labels)) as_labeller(facet_labels) else "label_value"
  
    # Build per-row color vector based on group_var
  get_color <- function(df) {
    if (is.null(color_map)) return(rep(color, nrow(df)))
    mapped <- color_map[as.character(df[[group_var]])]
    ifelse(is.na(mapped), color, mapped)
  }

  p <- ggplot(data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_point(
      size = 8,
      aes(
        color = .data[[group_var]],
        alpha = section
      )
    ) +
    scale_alpha_manual(values = c(sample1 = 0.8, sample2 = 0.3)) +
    geom_smooth(aes(color = .data[[group_var]]), alpha = 0.3, size = 0, method = "lm", show.legend = FALSE) +
    stat_smooth(aes(color = .data[[group_var]]), geom = "line", alpha = 0.9, size = 1.5, method = "lm", show.legend = FALSE) +
    scale_color_manual(
      values = setNames(
        sapply(levels(data[[group_var]]), function(g) if (!is.null(color_map) && g %in% names(color_map)) color_map[[g]] else color),
        levels(data[[group_var]])
      )
    ) +
    coord_cartesian(ylim = ylim) +
    geom_label_repel(
      data = label_data,
      aes(label = label),
      segment.alpha = 0.7,
      nudge_y = nudge_vals,
      force = 10, force_pull = 0.2, size = 4,
      segment.size = 1.2,
      point.padding = unit(1, "lines"),
      min.segment.length = 0,
      box.padding = unit(0.5, "lines"),
      max.overlaps = Inf,
      label.padding = unit(0.25, "lines"),
      label.r = unit(0.5, "lines"),
      show.legend = FALSE
    ) +
    ylab("Baseline-corrected\nproportion target looking") +
    xlab("Target-distractor embedding similarity") +
    scale_y_continuous(breaks = seq(-0.1, 0.2, by = 0.1)) +
    facet_wrap(
      facets = ~ .data[[group_var]],
      dir = facet_dir, strip.position = "top",
      labeller = labeller_fn,
      ncol = n_col, scales = "free"
    ) +
    guides(shape="none", color="none", alpha="none")+
    theme_classic() +
    theme(
      text = element_text(size = 16, face = "bold"),
      axis.title.x = element_text(face = "bold", size = 27, margin = margin(t = 15)),
      axis.title.y = element_text(face = "bold", size = 27, margin = margin(r = 20)),
      axis.text = element_text(size = 24, face = "bold"),
      legend.title = element_text(size = 22, face = "bold"),
      legend.text = element_text(size = 22, face = "bold"),
      legend.position = "bottom",
      legend.key = element_blank(),
      strip.text = element_text(size = 28, face = "bold"),
      strip.background = element_rect(fill = "gray90", color = NA),
      strip.text.x = element_text(margin = margin(t = 8, b = 8)),
      panel.spacing = unit(0.5, "cm")
    )
  
  if (!is.null(facet_scales_x)) {
    p <- p + facetted_pos_scales(x = facet_scales_x)
  }
  
  return(p)
}

dino_data <- looking_data_summarized |> left_join(all_similarities, by=c("Trials.targetImage"="text1", "Trials.distractorImage"="text2")) |> rename("BabyView Similarity"="dinov3.babyview_image_similarity")
group_vars = c("Trials.trialID", "Trials.targetImage", "Trials.distractorImage",  "image_similarity", "text_similarity", "BabyView Similarity", "section")
dino_data_summarized <- (summarized_data(
    dino_data,
    "Trials.trialID", 
    "corrected_target_looking", 
    group_vars
  ))
dino_data_long <- dino_data_summarized |>
  rename(
    `Text Similarity` = text_similarity,
    `Image Similarity` = image_similarity
  ) |>
  pivot_longer(
    cols = c("Text Similarity", "Image Similarity", "BabyView Similarity"),
    names_to = "sim_type",
    values_to = "similarity"
  ) |>
  mutate(
    sim_type = factor(
      sim_type,
      levels = c("Text Similarity", "Image Similarity",  "BabyView Similarity")
    )
  )

all_sections_plot <- multiple_similarity_effects_plot_refactored(
  dino_data_long,
  x_var = "similarity",
  group_var = "sim_type",
  input_title = "Looking time and embedding correlations",
  label_filter = "Trials.targetImage == 'acorn'",
  facet_scales_x = list(
    `Text Similarity` = scale_x_continuous(
          breaks = seq(0.7, 0.9, by = 0.1),
          limits = c(0.62, 0.93)
      ),
        `Image Similarity` = scale_x_continuous(
          breaks = seq(0.4, 0.8, by = 0.1),
          limits = c(0.38, 0.86)
      ),
    `Babyview Similarity` = scale_x_continuous(breaks = seq(0, 0.4, by = 0.1), limits = c(-0.1, 0.5))
  ),
  color_map = c("Text Similarity" = "#C76D48")
)
section_1_plot <- multiple_similarity_effects_plot_refactored(
  dino_data_long |> filter(section == "sample1"),
  x_var = "similarity",
  group_var = "sim_type",
  input_title = "Looking time and embedding correlations",
  label_filter = "Trials.targetImage == 'acorn' | Trials.distractorImage == 'acorn'",
  facet_scales_x = list(
    `Text Similarity` = scale_x_continuous(
          breaks = seq(0.75, 0.9, by = 0.05),
          limits = c(0.7, 0.91)
      ),
        `Image Similarity` = scale_x_continuous(
          breaks = seq(0.5, 0.9, by = 0.1),
          limits = c(0.45, 0.9)
      ),
    `BabyView-trained similarity` = scale_x_continuous(breaks = seq(0, 0.3, by = 0.1), limits = c(-0.05, 0.32))
  ),
  color_map = c("Text Similarity" = "#C76D48")
)
```

Decided not to use this plot since there was too much going on
```{r, fig.width=15.344, fig.height=5.799, fig.units="in"}
all_sections_plot
```

This is the plot we ended up using in the poster:
```{r, fig.width=15.344, fig.height=5.799, fig.units="in"}
section_1_plot
```

```{r}
ggsave(here("figures","cds","all_sections_similarity.svg"),all_sections_plot,width=15.344,height=4.799,units="in",bg = "white", device="pdf")
ggsave(here("figures","cds","section_1_similarity.svg"),section_1_plot,width=15.344,height=5.799,units="in",bg = "white", device="pdf")
ggsave(here("figures","cds","all_sections_similarity.png"),all_sections_plot,width=7,height=11.2,bg = "white")
ggsave(here("figures","cds","section_1_similarity.png"),section_1_plot,width=17,height=11.2,bg = "white")
#,`DINO similarity`          = scale_x_continuous(breaks = seq(0, 0.4, by = 0.1), limits = c(-0.1, 0.5))
```


# Saliency plots
```{r fig.width=15, fig.height=12}
# Prepare the data by combining both datasets with a grouping variable
trialid_level_summary <- summarized_data(target_looking_trial_level, "Trials.trialID", "corrected_target_looking", c("Trials.trialID", "section"))  |> left_join(trial_metadata)
baseline_looking_trial_level <- summarized_data(looking_data_summarized |> rename("mean_looking"="mean_target_looking_baseline_window"), "Trials.trialID", "mean_looking", c("Trials.trialID", "section")) |> left_join(trial_metadata) 

trialid_level_summary$plot_type <- "Baseline-corrected"
baseline_looking_trial_level$plot_type <- "Baseline window"

combined_data <- bind_rows(trialid_level_summary, baseline_looking_trial_level)

# Create labels for trials where target is acorn and distractor is coconut
combined_data$label_text <- ifelse(
  combined_data$Trials.targetImage == "acorn" & combined_data$Trials.distractorImage == "coconut",
  paste("Target:", combined_data$Trials.targetImage, "\nDistractor:", combined_data$Trials.distractorImage),
  ""
)

# Create the combined faceted plot
combined_saliency_plot <- ggplot(combined_data, aes(x = MeanSaliencyDiff, y = mean_value)) +
  geom_smooth(method = "lm", color = "#182B49", fill = "#182B49", alpha = 0.5) +
  geom_point(size = 8, color = "#182B49", aes(alpha=section)) +
  scale_alpha_manual(values = c(sample1 = 0.8, sample2 = 0.3)) +
  geom_label_repel(aes(label = label_text), 
                   color = "black", 
                   fill = "white", 
                   alpha = 0.8,
                         segment.alpha = 0.7,
      nudge_y = 0.02,
      force = 10,
      force_pull = 0.1,
      segment.size = 1.2,
                   size = 8) +
  facet_wrap(~ plot_type, scales = "free_y", ncol = 2) +
  xlab("Target-distractor GBVS mean saliency difference") +
  ylab("Proportion of target looking") +
  theme_minimal() +
  theme(
    text = element_text(size = 16, face = "bold"),
    axis.title.x = element_text(
      face = "bold", 
      size = 29,
      margin = margin(t = 15, r = 0, b = 0, l = 0)
    ),
    legend.key = element_blank(),
    axis.title.y = element_text(
      face = "bold", 
      size = 29,
      margin = margin(t = 0, r = 10, b = 0, l = 0)
    ),
    axis.text = element_text(size = 24, face = "bold"),
    legend.title = element_text(size = 22, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.position = "bottom",
    strip.text = element_text(size = 28, face = "bold"),
    strip.background = element_rect(fill = "gray90", color = NA),
    strip.text.x = element_text(margin = margin(t = 8, b = 8)),
    panel.spacing = unit(0.5, "cm") 
  ) 

# Display the plot
combined_saliency_plot

# Save the combined plot
ggsave(here("figures", "cds", "saliency_plot_poster_combined_alpha.svg"), 
       combined_saliency_plot, width = 15, height = 12, bg = "white", device = "pdf")

```

## Saliency lmers
The singular effect for the baseline window here throws me off. When I add in a random effect for the target image the effect disappears?
```{r}
## Baseline window looking
looking_data_summarized <- looking_data_summarized |>
  mutate(age_in_months = SubjectInfo.testAge / 30)

baseline_looking_image <- lmer(scale(mean_target_looking_baseline_window) ~ scale(MeanSaliencyDiff) 
                    + (1 | SubjectInfo.subjID)
                    + (1 | Trials.targetImage)
                    + (1 | Trials.ordinal)
                    + (1 | Trials.imagePair), 
                    data = looking_data_summarized)

baseline_looking_imagepair <- lmer(scale(mean_target_looking_baseline_window) ~ scale(MeanSaliencyDiff) 
                    + (1 | SubjectInfo.subjID)
                    + (1 | Trials.imagePair), 
                    data = looking_data_summarized)

critical_looking_image <- lmer(scale(mean_target_looking_critical_window) ~ scale(MeanSaliencyDiff)
                    + (1 | SubjectInfo.subjID)
                     + (1 | Trials.imagePair)
                    + (1 | Trials.targetImage), 
                    data = looking_data_summarized)

baseline_corrected_looking_image <- lmer(scale(corrected_target_looking) ~ scale(MeanSaliencyDiff)
                    + (1 | SubjectInfo.subjID)
                     + (1 | Trials.imagePair)
                    + (1 | Trials.targetImage), 
                    data = looking_data_summarized)

baseline_covariate_looking_image <- lmer(scale(mean_target_looking_critical_window) ~ scale(MeanSaliencyDiff)
                    + scale(mean_target_looking_baseline_window)
                    + (1 |  SubjectInfo.subjID) 
                    + (1 | Trials.imagePair)
                    + (1|Trials.targetImage), 
                    data = looking_data_summarized)


summary(baseline_looking_image)
summary(baseline_looking_imagepair)
summary(critical_looking_image)
summary(baseline_corrected_looking_image)
summary(baseline_covariate_looking_image)
```

Do we see an interaction with window type?
```{r}
trials_window_type_separated <- looking_data_summarized |>
  pivot_longer(cols=c(mean_target_looking_critical_window, mean_target_looking_baseline_window), names_to="window_type", values_to="target_looking") |>
  mutate(window_type = str_replace(window_type, "mean_target_looking_", "")) |>
  mutate(trial_window_c = case_when(
    window_type=="critical_window" ~ 0.5,
    window_type=="baseline_window" ~ -0.5))

window_type_looking <- lmer(scale(target_looking) ~ trial_window_c*scale(MeanSaliencyDiff) + 
                    + scale(AoA_Est_target)
                    + (1 | SubjectInfo.subjID) 
                    + (1 | Trials.ordinal)
                    + (1 | Trials.targetImage), 
                    data = trials_window_type_separated)

summary(window_type_looking)
```
I could check the difference between baseline window looking and baseline-corrected looking even though that is a little strange
```{r}
trials_window_type_separated_baselinecorrected <- looking_data_summarized |>
  mutate(corrected_target_looking = scale(corrected_target_looking),
         mean_target_looking_baseline_window = scale(mean_target_looking_baseline_window)) |>
  pivot_longer(cols=c(corrected_target_looking, mean_target_looking_baseline_window), names_to="window_type", values_to="target_looking") |>
  mutate(window_type = str_replace(window_type, "mean_target_looking_", "")) |>
  mutate(trial_window_c = case_when(
    window_type=="corrected_target_looking" ~ 0.5,
    window_type=="baseline_window" ~ -0.5))

window_type_looking_baselinecorrected <- lmer(scale(target_looking) ~ trial_window_c*scale(MeanSaliencyDiff) + 
                    + (1 | SubjectInfo.subjID)
                    + (1 | Trials.targetImage), 
                    data = trials_window_type_separated_baselinecorrected)

summary(window_type_looking_baselinecorrected)
```

Collapsing across trial types
```{r}
looking_data_summarized_image_pair <- looking_data_summarized %>%
  mutate(across(
    c(mean_target_looking_baseline_window, MeanSaliencyDiff),
    ~ ifelse(grepl("distractor", Trials.trialID), -.x, .x)
  ))
baseline_looking_collapsed <- lmer(scale(mean_target_looking_baseline_window) ~ scale(MeanSaliencyDiff)
                    + (1 | SubjectInfo.subjID)
                    + (1 | Trials.imagePair), 
                    data = looking_data_summarized_image_pair)
summary(baseline_looking_collapsed)
```

checking variance across predictors
```{r}
looking_data_summarized %>%
  group_by(Trials.targetImage) %>%
  summarize(var_saliency = var(MeanSaliencyDiff),
            var_similarity = var(image_similarity))
```

what about across excluded participants as well: this is a little sketchy.
```{r}
baseline_looking_image_full_sample <- lmer(scale(mean_target_looking_baseline_window) ~ scale(MeanSaliencyDiff)
                    + (1 | SubjectInfo.subjID)
                    + (1 | Trials.targetImage)
                    + (1 | Trials.imagePair), 
                    data = trial_summary_data |> left_join(trial_metadata))


summary(baseline_looking_image_full_sample)
```


## saliency order effects
this is interesting! order effects showing up in the baseline window
```{r}
order_ranked_trials <- looking_data_summarized |>
  group_by(SubjectInfo.subjID, Trials.targetImage) |>
  arrange(Trials.ordinal, .by_group = TRUE) |>
  mutate(
    slice_num = row_number(),
    order = case_when(
      slice_num == 1 ~ -0.5,
      slice_num == 2 ~ 0.5,
      TRUE ~ NA
    )
  )
main_image_effect_ranked <- lmer(scale(mean_target_looking_baseline_window) ~ (scale(order))
                    + scale(age_in_months)
                    + scale(MeanSaliencyDiff)                                     
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage), 
                    data = order_ranked_trials |> mutate(age_in_months = SubjectInfo.testAge / 30))
# |> filter(Trials.trialType %in% c("easy", "hard")
summary(main_image_effect_ranked)

looking_data_first_appearance <- looking_data_summarized |>
  group_by(SubjectInfo.subjID, Trials.targetImage) |>
  arrange(Trials.ordinal, .by_group = TRUE) |>
  slice(1) |>
  ungroup()

baseline_looking_first_appearance_model <- lmer(scale(mean_target_looking_baseline_window) ~ scale(MeanSaliencyDiff) 
                    + (1 | SubjectInfo.subjID)
                    + (1 | Trials.targetImage)
                    + (1 | Trials.imagePair), 
                    data = looking_data_first_appearance)
# |> filter(Trials.trialType %in% c("easy", "hard")
summary(baseline_looking_first_appearance_model)
```

# OpenCLIP training
- Used CCN 2025 version of this plot.

