```{r echo=FALSE}
library(tidyverse)
library(here)
library(reticulate)
library(dotenv)
library(readr)
library(gghalves)
#devtools::install_github("langcog/wordbankr")
library(ggrepel)
library(relayer) # devtools::install_github("clauswilke/relayer")
library(viridis)
library(RColorBrewer)
library(lmerTest)
library(cowplot)
library(ggtext)
source("helpers.R")

load_dot_env(file=here(".env"))
PROJECT_VERSION = Sys.getenv("PROJECT_VERSION")
```

### Load data
```{r}
PROCESSED_DATA_PATH = here("data",PROJECT_VERSION,"processed_data")
looking_time_resampled_clean <- read.csv(file.path(PROCESSED_DATA_PATH, "level-looks_data.csv"))
all_looking_times <- read.csv(file.path(PROCESSED_DATA_PATH,"level-looks_added-metadata_data.csv"))
trial_metadata <- read.csv(here("data","metadata","level-trialtype_data.csv"))
trial_summary_data <- read.csv(file.path(PROCESSED_DATA_PATH,"level-trials_data.csv"))
# TODO: move similarity correlations to exploratory qmd file
cvcl_similarities <- read.csv(here("data", "embeddings", "similarities-cvcl_data.csv"))
openclip_similarities <- read.csv(here("data", "embeddings", "similarities-openclip_data.csv"))
saycamvit_similarities <- read.csv(here("data", "embeddings", "similarities-saycamvit_data.csv"))
imagenetvit_similarities <- read.csv(here("data", "embeddings", "similarities-imagenetvit_data.csv"))
looking_data_summarized <- trial_summary_data |>
  filter(trial_exclusion == 0 & exclude_participant == 0 & exclude_participant_insufficient_data == 0) |>
  left_join(trial_metadata) |>
  arrange(AoA_Est_target)

mean_age <- looking_data_summarized %>%
  distinct(SubjectInfo.subjID, .keep_all = TRUE) %>%  # Keep only distinct subjects
  summarize(overall_mean_age = mean(SubjectInfo.testAge, na.rm = TRUE))  %>%
  pull(overall_mean_age) / 30

mean_age <- round(mean_age, 2)
```

util function to see what the order of trials were for individual participants
```{r}
order_of_trials <- function(data, subjID) {
  curr_order <- data |>
  filter(SubjectInfo.subjID == subjID) |>
  distinct(Trials.trialID, .keep_all=TRUE) |>
  arrange(Trials.ordinal) |>
  select(Trials.ordinal, Trials.trialID, Trials.targetImage, Trials.distractorImage, Trials.trialType, Trials.leftImage, Trials.rightImage, Trials.targetAudio)
  write_csv(curr_order, paste0(subjID,".csv"))
}

#order_of_trials(all_looking_times, "L7Y4Y6")
```

### Overall timecourse plot of proportion target looking 
```{r}
#summarizing within subject for each time point
summarize_subj <- looking_time_resampled_clean %>%
  filter(trial_exclusion == 0 & exclude_participant ==0 & exclude_participant_insufficient_data == 0) %>%
  filter(!is.na(accuracy_transformed)) %>%
  group_by(SubjectInfo.subjID, time_normalized_corrected, SubjectInfo.testAge) %>%
  filter(n() > 10) %>%
  summarized_data(., "SubjectInfo.subjID", "accuracy_transformed", c("SubjectInfo.testAge", "time_normalized_corrected")) %>%
  rename(mean_accuracy = mean_value)

#summarizing across subjects for each time point
summarize_across_subj <- summarize_subj %>%
  group_by(time_normalized_corrected) %>%
  filter(n() > 10) %>%
  summarized_data(., "time_normalized_corrected", "mean_accuracy", c("time_normalized_corrected")) |>
  rename(accuracy = mean_value)

looking_times <- ggplot(summarize_across_subj,aes(time_normalized_corrected,accuracy))+
  xlim(-2000,4000)+
  geom_errorbar(aes(ymin=accuracy-ci,ymax=accuracy+ci),width=0, alpha=0.2)+
  #geom_point(alpha=0.2)+
    geom_smooth(method="gam")+
  geom_vline(xintercept=0,size=1.5)+
  geom_hline(yintercept=0.5,size=1.2,linetype="dashed")+
  geom_vline(xintercept=300,linetype="dotted")+
  ylim(0,1)+
  xlab("Time (normalized to target word onset) in ms")+
  ylab("Proportion Target Looking")
looking_times
ggsave(here("figures",PROJECT_VERSION,"prop_looking_across_time.png"),looking_times,width=9,height=6,bg = "white")
```

## Descriptive plots
#### Usable trial stats
```{r}
#Overall baseline-corrected proportion target looking by condition
looking_data_exclusions <- trial_summary_data |>
  mutate(trial_exclusion_reason = as.factor(ifelse(is.na(trial_exclusion_reason), "included", trial_exclusion_reason))) |>
  mutate(trial_exclusion_reason = factor(trial_exclusion_reason, levels=c(setdiff(unique(trial_exclusion_reason), "included"), "included")))

# Compute the number of included trials per subject
included_counts <- looking_data_exclusions |>
  filter(trial_exclusion_reason == "included") |>
  count(SubjectInfo.subjID, name = "included_trials")


excluded_subjects <- setdiff(unique(looking_data_exclusions$SubjectInfo.subjID), 
                             unique(looking_data_summarized$SubjectInfo.subjID))

# Ensure all subjects are included and replace NA with 0
exclusions_by_subject <- looking_data_exclusions |>
  summarize(N = n(), .by = c(SubjectInfo.subjID, trial_exclusion_reason)) |>
  left_join(included_counts, by = "SubjectInfo.subjID") |>
  mutate(included_trials = replace_na(included_trials, 0)) |>  # Replace NA values
  # Ordering subject IDs so that the 'red' colored label to mark excluded subjects is placed on the subjects who are actually excluded
  mutate(SubjectInfo.subjID = factor(SubjectInfo.subjID, 
                                     levels = unique(SubjectInfo.subjID[order(-included_trials)])),
         color = ifelse(SubjectInfo.subjID %in% excluded_subjects, "red", "black")) |>
  arrange(color)

looking_data_exclusions_combined <- looking_data_exclusions |>
  summarize(N = n(),
    .by=c(trial_exclusion_reason))
# Format labels with HTML <span> for colors

exclusions_color_labels <- exclusions_by_subject |> 
  distinct(SubjectInfo.subjID, .keep_all = TRUE) |>
  mutate(colored_labels = paste0("<span style='color:", color, "'>", SubjectInfo.subjID, "</span>"))

ggplot(exclusions_by_subject, aes(x = SubjectInfo.subjID, y = N, fill = trial_exclusion_reason)) +
  geom_bar(stat = "identity", position = "stack") +  
  labs(x = "Subject ID", y = "Count (N)", title = "Trial Exclusions by Subject", fill = "Trial Exclusion Reason") +
  theme_minimal() +  
  theme(
    axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1),  # Enable HTML-styled labels
    strip.text = element_text(size = 8)
  ) +
  scale_x_discrete(labels = exclusions_color_labels$colored_labels) +  # Apply colored labels
  scale_fill_brewer(palette = "Set3")


#TODO: we have a participant who participated twice but their first session only had 2 trials. figure out how to deal with this/discard first session trials. Also have to figure out how to deal with participants who are excluded by default
```


#### Estimating item and subject-level noise
```{r}
target_looking_item_subject_level <- summarized_data(looking_data_summarized, "Trials.targetImage", "corrected_target_looking", c("SubjectInfo.subjID", "SubjectInfo.testAge", "AoA_Est_target"))

target_looking_item_level <- summarized_data(target_looking_item_subject_level |> rename(mean_target_looking = mean_value), "Trials.targetImage", "mean_target_looking", "AoA_Est_target")

target_looking_item_age_level <- summarized_data(target_looking_item_subject_level |> rename(mean_target_looking = mean_value) |> add_age_split(), "Trials.targetImage", "mean_target_looking", c("AoA_Est_target", "age_half"))

target_looking_trial_subject_level <- summarized_data(looking_data_summarized, "Trials.trialID", "corrected_target_looking", c("SubjectInfo.subjID", "SubjectInfo.testAge", "AoA_Est_distractor", "AoA_Est_target", "Trials.targetImage", "Trials.distractorImage", "Trials.imagePair"))

target_looking_trial_level <- summarized_data(target_looking_trial_subject_level |> rename(mean_target_looking = mean_value), "Trials.trialID", "mean_target_looking", c("AoA_Est_distractor", "AoA_Est_target", "Trials.targetImage", "Trials.distractorImage", "Trials.imagePair"))

target_looking_subject_level <- summarized_data(looking_data_summarized, "SubjectInfo.subjID", "corrected_target_looking", "SubjectInfo.testAge")
```

#### Item-level performance
```{r}
item_performances <- ggplot(target_looking_item_level, aes(reorder(Trials.targetImage, mean_value), mean_value)) +
   geom_hline(yintercept=0,linetype="dashed")+
  geom_errorbar(aes(ymin=lower_ci,ymax=upper_ci),width=0, alpha=0.2)+
  (geom_point(aes(aoa_size=AoA_Est_target)) |> rename_geom_aes(new_aes = c("size" = "aoa_size")))+
  (geom_jitter(data=target_looking_item_subject_level, aes(x=Trials.targetImage, y=mean_value, color=SubjectInfo.subjID, age_size = SubjectInfo.testAge/30), alpha=0.3, width=0.2) |> rename_geom_aes(new_aes = c("size" = "age_size"))) +
  xlab("Target image")+
  ylab("Proportion of target looking")+
  ggtitle("Mean proportion of target looking across target items") +
  theme(axis.title.x = element_text(face="bold", size=15, vjust=-1),
        axis.text.x  = element_text(size=10,angle=0,vjust=0.5),
        axis.title.y = element_text(face="bold", size=15),
        axis.text.y  = element_text(size=10),
        strip.text.x = element_text(size = 10,face="bold"),
        plot.margin = margin(t = 10, r = 10, b = 30, l = 10)
        ) +
  scale_y_continuous(breaks = seq(-1, 1, by = 0.2)) +
  scale_size_c(aesthetics = "age_size",name = "Age of participant in months", range=c(2,4), guide = guide_legend(order = 2)) +
  scale_size_c( aesthetics = "aoa_size",name = "Est. AoA of target words in years", guide = guide_legend(order = 1)) +
  scale_color_viridis_d(name = "Participant IDs",option="D") +
  guides(
    color = "none"
  ) 
item_performances
ggsave(here("figures",PROJECT_VERSION,"item_performances.png"),item_performances,width=15,height=10,bg = "white")

trial_performances <- ggplot(summarized_data(looking_data_summarized, "Trials.trialID", "corrected_target_looking", c("Trials.trialID", "AoA_Est_target")), aes(reorder(Trials.trialID, mean_value), mean_value)) +
   geom_hline(yintercept=0,linetype="dashed")+
  geom_errorbar(aes(ymin=lower_ci,ymax=upper_ci),width=0, alpha=0.2)+
  (geom_point(aes(aoa_size=AoA_Est_target)) |> rename_geom_aes(new_aes = c("size" = "aoa_size")))+
  (geom_jitter(data=looking_data_summarized,aes(x=Trials.trialID, y=corrected_target_looking, color=SubjectInfo.subjID, age_size = SubjectInfo.testAge/30), alpha=0.3, width=0.2) |> rename_geom_aes(new_aes = c("size" = "age_size"))) +
  xlab("Trial type")+
  ylab("Proportion of target looking")+
  ggtitle("Mean proportion of target looking across trial types") +
  scale_size_c(aesthetics = "age_size",name = "Age of participant in months", range=c(2,4), guide = guide_legend(order = 2)) +
  scale_size_c( aesthetics = "aoa_size",name = "Est. AoA of target words in years", guide = guide_legend(order = 1)) +
  scale_color_viridis_d(name = "Participant IDs",option="D") +
  coord_cartesian(ylim = c(-1, 1)) +
    theme(axis.title.x = element_text(face="bold", size=15, vjust=-1),
        axis.text.x  = element_text(size=8,angle=45,hjust=1),
        axis.title.y = element_text(face="bold", size=15),
        axis.text.y  = element_text(size=15),
        strip.text.x = element_text(size = 10,face="bold"),
        aspect.ratio = 1,
        plot.margin = margin(t = 10, r = 10, b = 30, l = 10)
        ) +
  guides(
    color = "none"
  ) 
trial_performances
```

## Age plots 

#### Age-split timecourses
```{r}
 
summarize_across_age_halves <- summarize_subj |> add_age_split() |>
  group_by(time_normalized_corrected, age_half) |>
  dplyr::summarize(n=n(),
            non_na_n = sum(!is.na(mean_accuracy)),
            mean_value=mean(mean_accuracy,na.rm=TRUE),
            sd_accuracy=sd(mean_accuracy,na.rm=TRUE),
            se_accuracy=sd_accuracy/sqrt(n),
            ci = ifelse(n > 1, qt(0.975, n - 1) * sd_accuracy / sqrt(n), NA)) %>%
  filter(n > 5)

looking_times_age <- ggplot(summarize_across_age_halves,aes(time_normalized_corrected,mean_value,color=age_half))+
  xlim(-2000,4000)+
  geom_errorbar(aes(ymin=mean_value-ci,ymax=mean_value+ci),width=0, alpha=0.2)+
  #geom_point(alpha=0.2)+
    geom_smooth(method="gam")+
  geom_vline(xintercept=0,size=1.5)+
  geom_hline(yintercept=0.5,size=1.2,linetype="dashed")+
  geom_vline(xintercept=300,linetype="dotted")+
  ylim(0,1)+
  xlab("Time (normalized to target word onset) in ms")+
  ylab("Proportion Target Looking") +
  labs(title="Proportion of looking time across age and time", caption = (paste0("14-24 month olds age split at M=",mean_age," months"))) +
  scale_color_brewer(palette = "Set1", name="Age half")

looking_times_age

ggsave(here("figures",PROJECT_VERSION,"prop_looking_across_time_age.png"),looking_times,width=9,height=6,bg = "white")
```

#### Age-split performance
```{r}
# note: using shorter window just 
participant_age_halves = summarized_data(looking_data_summarized |> left_join(target_looking_item_level) |> rename(mean_looking = mean_value) |>  add_age_split() |> mutate(acc = corrected_target_looking_short + 0.5), "age_half", "acc", 
                                         c("age_half", "SubjectInfo.subjID", "SubjectInfo.testAge")) 


participant_age_halves$age_half <- factor(participant_age_halves$age_half, levels = rev(levels(factor(participant_age_halves$age_half))))

participant_age_halves_summarized = summarized_data(participant_age_halves |> rename(looking_time = mean_value), "age_half", "looking_time", c("age_half"))
accuracy_age <- ggplot(participant_age_halves,
       aes(x = age_half, y = mean_value, color = age_half)) +
    geom_violin(aes(color=age_half), alpha=0.3) +
  geom_jitter(size = 3, alpha = 0.3, width=0.2) +
  geom_hline(yintercept=0.5,size=1.2,linetype="dashed")+ 
  geom_point(data = participant_age_halves_summarized, size = 3) +
  geom_linerange(data = participant_age_halves_summarized, aes(ymin = mean_value - ci, ymax = mean_value + ci), alpha = 0.9) + 
  scale_color_brewer(palette = "Set1", name="Age half", direction=-1) +  # Using RColorBrewer for colors
  ylab("Accuracy") +
  xlab("Age half of child") +
  ggpubr::stat_cor(method = "pearson") +
  labs(caption = (paste0("14-24 month olds age split at M=",mean_age, " months")), title="Word recognition acuracy by age")
accuracy_age
ggsave(here("figures",PROJECT_VERSION,"accuracy_age.png"),accuracy_age,width=9,height=6,bg = "white")
```

#### Age continuous
```{r}
ggplot(participant_age_halves, aes(x = SubjectInfo.testAge/30, y = mean_value)) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_point(size = 4, alpha = 0.4,
             position = position_jitter(width = 0.1, seed = 123)) +
  geom_smooth() +
  scale_y_continuous(breaks = seq(0.3, 0.8, by = 0.1), limits = c(0.3, 0.8)) +
  labs(x = "Age in months", y = "Accuracy") +
  ggtitle("Corrected proportion of target looking by age") +
  theme_minimal() +
  ggpubr::stat_cor(method = "pearson")
```
younger group mean
```{r}
younger_mean <- participant_age_halves |>
  filter(age_half == "younger") |>
  summarize(mean_value = mean(SubjectInfo.testAge)/30) |>
  pull(mean_value)
```
## Easy vs hard trial plots

#### Proportion of target looking for easy vs hard trials
```{r}
avg_corrected_target_looking_by_condition <- summarized_data(looking_data_summarized,
                                                             "Trials.trialType", "corrected_target_looking", "SubjectInfo.subjID")
high_accuracy_subjects <- avg_corrected_target_looking_by_condition |>
  filter(lower_ci > 0) |>
  distinct(SubjectInfo.subjID)

overall_condition_plot <- half_violins_plot(looking_data_summarized |> filter(Trials.trialType == "easy" | Trials.trialType == "hard"), "Trials.trialType", "corrected_target_looking", "SubjectInfo.subjID", c("easy", "hard"))
overall_condition_plot
ggsave(here("figures",PROJECT_VERSION,"condition_based_looking.png"),overall_condition_plot,width=9,height=6,bg = "white")
```

#### Target image difficulty
```{r}
# summarize average accuracy within participant (by word alone)
condition_based_looking <- looking_data_summarized  |>
  filter(!grepl("distractor", Trials.trialType)) |>
  distinct(SubjectInfo.subjID, Trials.trialID, Trials.targetImage, corrected_target_looking, Trials.trialType, AoA_Est_target)

target_looking_by_target_word <- looking_data_summarized  |>
  filter(!grepl("distractor", Trials.trialType)) |>
  group_by(SubjectInfo.subjID, Trials.targetImage) |>
  summarize(target_looking_diff = corrected_target_looking[match("easy", Trials.trialType)] - corrected_target_looking[match("hard", Trials.trialType)],
            baseline_window_looking_diff = mean_target_looking_baseline_window[match("easy", Trials.trialType)] - mean_target_looking_baseline_window[match("hard", Trials.trialType)], 
            critical_window_looking_diff = mean_target_looking_critical_window[match("easy", Trials.trialType)] - mean_target_looking_critical_window[match("hard", Trials.trialType)]) |>
  filter(!is.na(target_looking_diff))

#clean names for individual images for plot
overall_target_looking_by_word <- target_looking_by_target_word %>%
  filter(!is.na(target_looking_diff)) %>%
  group_by(Trials.targetImage) %>%
  summarize(N=n(),
            corrected_target_looking=mean(target_looking_diff,na.rm=TRUE),
            ci=qt(0.975, N-1)*sd(target_looking_diff,na.rm=T)/sqrt(N),
            lower_ci=corrected_target_looking-ci,
            upper_ci=corrected_target_looking+ci
          ) 


word_prefs <- ggplot(overall_target_looking_by_word,aes(reorder(Trials.targetImage,corrected_target_looking),corrected_target_looking))+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_errorbar(aes(ymin=lower_ci,ymax=upper_ci),width=0, alpha=0.3)+
  geom_jitter(data=target_looking_by_target_word, aes(x=Trials.targetImage, y=target_looking_diff, color=SubjectInfo.subjID), size = 2.5, alpha = 0.3, width=0.1) +
  geom_point(size = 2.4)+
  xlab("Target Word")+
  ylab("Easy trial prefered target looking")+
  theme(axis.title.x = element_text(face="bold", size=15),
        axis.text.x  = element_text(size=10,angle=90,vjust=0.5,hjust=1),
        axis.title.y = element_text(face="bold", size=15),
        axis.text.y  = element_text(size=10),
        strip.text.x = element_text(size = 10,face="bold")
        ) +
  scale_y_continuous(breaks = seq(-1, 1, by = 0.2)) +
  scale_size_continuous(name = "Number of participants") + 
  scale_color_viridis_d(name = "Participant IDs",option="D") +
  guides(color = "none")
  
word_prefs
ggsave(here("figures",PROJECT_VERSION,"easy_trial_pref_by_word.png"),word_prefs,width=9,height=6,bg = "white")

```


#### Baseline image-pair preferences
```{r}
saliency_effects <- looking_data_summarized |>
  # Calculating the proportion of time looking at the target word even if it isn't the target word in that particular study
 mutate(original_target_looking_baseline_window = ifelse(grepl("distractor", Trials.trialType), 1 - mean_target_looking_baseline_window,   mean_target_looking_baseline_window),
        original_target_looking_critical_window = ifelse(grepl("distractor", Trials.trialType), 1 - mean_target_looking_critical_window, mean_target_looking_critical_window)) |>
  add_age_split() |>
 summarize(mean_baseline_looking = mean(original_target_looking_baseline_window),
           mean_critical_looking = mean(original_target_looking_critical_window),
           .by = c(Trials.imagePair, age_half))
```

## CLIP similarity plots
Comparing proportion of target looking time to CLIP and other model cosine similarities
```{r}
# CLIP
clip_data_summarized <- summarize_similarity_data(looking_data_summarized)

clip_age_half_summarized <- looking_data_summarized |>
  add_age_split() |>
  summarize_similarity_data(extra_fields = c("age_half"))

clip_plots <- generate_multimodal_plots(clip_data_summarized, "CLIP")
clip_age_plots <- generate_multimodal_age_effect_plots(clip_age_half_summarized, model_type="CLIP")
clip_plots
clip_age_plots

# CVCL
create_model_plots(cvcl_similarities, name="CVCL")
create_model_plots(imagenetvit_similarities, name="ImageNetVIT")
create_model_plots(saycamvit_similarities, name="SayCamVIT")
```

#### OpenCLIP training  

```{r}
openclip_similarities_combined <- openclip_similarities |>
  rename(word_a = word1, word_b = word2) |>
  bind_rows(
    openclip_similarities |>
      rename(word_a = word2, word_b = word1)
  )
looking_data_w_openclip <- looking_data_summarized |>
  select(-text_similarity, -multimodal_similarity, -image_similarity) |>
  left_join(openclip_similarities_combined, by = c("Trials.distractorImage"="word_a", "Trials.targetImage"="word_b"))

openclip_data_summarized <- summarize_similarity_data(looking_data_w_openclip, extra_fields=c("epoch"))
openclip_age_half_summarized <- looking_data_w_openclip |>
  add_age_split() |>
  summarize_similarity_data(extra_fields = c("age_half", "epoch"))

# Function to calculate Pearson's correlation per epoch
calculate_correlations <- function(data, x_var, y_var, group_var = c("epoch"), conf_level = 0.95) {
  data |>
    group_by(across(all_of(group_var))) |>
    summarize(
      {
        cor_test <- cor.test(.data[[x_var]], .data[[y_var]], method = "pearson", conf.level = conf_level)
        tibble(
          pearson_cor = cor_test$estimate,
          p_value = cor_test$p.value,
          ci_lower = cor_test$conf.int[1],
          ci_upper = cor_test$conf.int[2]
        )
      },
      .groups = "drop"
    )
}

image_correlation_results_age_split <- calculate_correlations(openclip_age_half_summarized, "image_similarity", "mean_value", group_var=c("epoch", "age_half"))

text_correlation_results <- calculate_correlations(openclip_data_summarized, "text_similarity", "mean_value")
image_correlation_results <- calculate_correlations(openclip_data_summarized, "image_similarity", "mean_value")

ggplot(image_correlation_results, aes(x = epoch, y = pearson_cor)) +
  geom_point(aes(color = p_value < 0.05), size = 3) + 
  geom_smooth(span = 2) +
  labs(title = "Image similarity correlation across Open-CLIP training",
       x = "Epoch",
       y = "Pearson Correlation") +
  scale_color_manual(values = c("TRUE" = "black", "FALSE" = "gray")) +  # Set color for significance
  theme_minimal() +
  theme(legend.position = "none")

ggplot(text_correlation_results, aes(x = epoch, y = pearson_cor)) +
  geom_point(aes(color = p_value < 0.05), size = 3) + 
  geom_smooth(span = 2) +
  labs(title = "Word similarity correlation across Open-CLIP training",
       x = "Epoch",
       y = "Pearson Correlation") +
  scale_color_manual(values = c("TRUE" = "black", "FALSE" = "gray")) +  # Set color for significance
  theme_minimal() +
  theme(legend.position = "none")


image_openclip_age <- epoch_age_half_plot(calculate_correlations(openclip_age_half_summarized, "image_similarity", "mean_value", group_var=c("epoch", "age_half")), "image_similarity")
text_openclip_age <- epoch_age_half_plot(calculate_correlations(openclip_age_half_summarized, "text_similarity", "mean_value", group_var=c("epoch", "age_half")), "text_similarity")
image_openclip_age
text_openclip_age
ggsave(here("figures",PROJECT_VERSION,"openclip_image_embeddings_age.png"),image_openclip_age,width=9,height=6,bg = "white")

``` 

#### Examining linear correlation between similarity types
```{r}
cor(data.frame(trial_metadata$multimodal_similarity, trial_metadata$image_similarity, trial_metadata$text_similarity, trial_metadata$cor))
cor.test(trial_metadata$image_similarity, trial_metadata$text_similarity)
cor.test((imagenetvit_similarities |> arrange(word1, word2))$image_similarity, (trial_metadata |> distinct(Trials.imagePair, .keep_all=TRUE) |> arrange(Trials.imagePair))$image_similarity, method="spearman")
# TODO: add direct similarity matrix 
```
# AoA plots
```{r}

ggplot(target_looking_item_level, aes(x=AoA_Est_target, y=mean_value))+
  geom_hline(yintercept=0,linetype="dashed")+
  geom_point(size=2, alpha=0.6)+
  geom_smooth(method="lm")+
  geom_label_repel(aes(label=ifelse(AoA_Est_target > 5.5 | AoA_Est_target < 4, Trials.targetImage, ""))) +
  xlab("Estimated AoA of target words")+
  ylab("Baseline-corrected prop. of target looking")+
  #ggtitle("Prop. of target looking by estimated AoA of target words")+
  theme_minimal()+
  theme(axis.title.x = element_text(face="bold", size=15, vjust=-1),
        axis.text.x  = element_text(size=10,angle=0,vjust=0.5),
        axis.title.y = element_text(face="bold", size=15),
        axis.text.y  = element_text(size=10),
        strip.text.x = element_text(size = 10,face="bold")
        ) +
 scale_x_continuous(breaks = seq(3, 6, by = 0.5)) +
  ggpubr::stat_cor(method = "spearman", label.y = max(target_looking_item_level$mean_value) + 0.05) +
 scale_color_brewer(palette = "Set2", name="Age half")

age_half_plot(target_looking_item_age_level, "AoA_Est_target", x_label="AoA of target word", title="Target looking by estimated AoA of target word across age half")


ggplot(target_looking_trial_level, aes(x=AoA_Est_distractor, y=mean_value)) +
  geom_point()+
  geom_label_repel(aes(label=Trials.imagePair)) +
  geom_smooth(method="gam")+
  geom_hline(yintercept=0,linetype="dashed")+
  xlab("Estimated AoA of distractor words")+
  ylab("Baseline-corrected prop. of target looking")+
  ggtitle("Prop. of target looking by estimated AoA of distractor words")+
  theme_minimal()+
  theme(axis.title.x = element_text(face="bold", size=15, vjust=-1),
        axis.text.x  = element_text(size=10,angle=0,vjust=0.5),
        axis.title.y = element_text(face="bold", size=15),
        axis.text.y  = element_text(size=10),
        strip.text.x = element_text(size = 10,face="bold"),
        
        ) +
  ggpubr::stat_cor(method = "spearman")
hist(target_looking_item_level$AoA_Est_target)


```

```{r}
mean_aoa <- mean(trial_metadata |> distinct(AoA_Est_target) |> pull(AoA_Est_target)) |> round(2)

aoa_data <- looking_data_summarized |> add_aoa_split() 
aoa_data$aoa_half <- factor(aoa_data$aoa_half, levels = c("lower", "higher"))

aoa_plot <- half_violins_plot(aoa_data, "aoa_half", "corrected_target_looking", "SubjectInfo.subjID", c("lower", "higher"), input_xlab = "Age-of-acquisition of target word", input_caption=paste0("AoA split at M=", mean_aoa))
aoa_plot
```

# Saliency correlations
```{r}
target_looking_trial_age_level <- summarized_data(target_looking_trial_subject_level |> rename(mean_target_looking = mean_value) |> add_age_split(), "Trials.trialID", "mean_target_looking", c("AoA_Est_target", "age_half"))
trialid_age_level_summary <- target_looking_trial_age_level |> left_join(trial_metadata)
trialid_level_summary <- target_looking_trial_level |> left_join(trial_metadata)

age_half_plot(trialid_age_level_summary, "MeanTargetSaliency", x_label="Mean target saliency")
age_half_plot(trialid_age_level_summary, "MeanSaliencyDiff", x_label="Mean saliency difference", title="Target looking by mean saliency difference across age and trial types")

target_looking_image_pair <- summarized_data(looking_data_summarized, "Trials.imagePair", "corrected_target_looking", c("SubjectInfo.subjID", "SubjectInfo.testAge"))
target_looking_imagepair_level <- summarized_data(target_looking_image_pair |> rename("mean_looking"="mean_value") |> add_age_split(), "Trials.imagePair", "mean_looking", c("age_half")) |> left_join(trial_metadata |> distinct(Trials.imagePair, .keep_all=TRUE)) |> mutate(MeanSaliencyDiff = abs(MeanSaliencyDiff))
age_half_plot(target_looking_imagepair_level, "MeanSaliencyDiff", x_label="Mean saliency difference", title="Target looking by mean saliency difference across age half and image pairs")
```


