---
title: "Main visual precision statistics"
format:
  html:
    toc: true
    toc-expand: 2
    toc-depth: 3
---
```{r message=FALSE}
library(tidyverse)
library(here)
library(lmerTest)
library(MuMIn)
library(lme4)
library(dotenv)
library(broom)
library(broom.mixed)
library(effects)
library(emmeans)

env_file = here(".env")
if (file.exists(env_file)) {
  load_dot_env(file = env_file)
  PROJECT_VERSION <- Sys.getenv("PROJECT_VERSION")
  if (PROJECT_VERSION == "") PROJECT_VERSION <- "main"
} else {
  PROJECT_VERSION <- "main"
}

VALID_SECTIONS <- c("sample1", "sample2")
DATA_FOLDER    <- if (PROJECT_VERSION %in% c(VALID_SECTIONS, "main")) "main" else PROJECT_VERSION
SECTION_FILTER <- if (PROJECT_VERSION %in% VALID_SECTIONS) PROJECT_VERSION else NULL
source("lmer_helpers.R")
```

# Load data
```{r}
trial_metadata <- read.csv(here("data","metadata","level-trialtype_data.csv"))
trial_summary_data <- read.csv(here("data", DATA_FOLDER, "processed_data", "level-trials_data.csv"))
bv_dino_similarities <- read.csv(here("data", "embeddings", "similarities-dinobv_data.csv"))
dinov3_similarities <- read.csv(here("data", "embeddings", "similarities-dino_data.csv"))

usable_trials <- trial_summary_data |>
  # excluding possible scam participant
  filter(exclude_participant_insufficient_data == 0 & trial_exclusion == 0 & exclude_participant == 0 & SubjectInfo.subjID != "PH2RNZ")

# Merging with similarity information and mean-centering main effects
trials_with_effect_vars <- usable_trials |>
  left_join(trial_metadata) |>
  mutate(age_in_months = SubjectInfo.testAge/30) |>
  left_join(bv_dino_similarities |> transmute(Trials.imagePair = paste0(word1, "-", word2), image_similarity_bv =  image_similarity)) |>
  left_join(dinov3_similarities |> transmute(Trials.imagePair = paste0(word1, "-", word2), image_similarity_dinov3 =  image_similarity))
  

# Filter by section if PROJECT_VERSION specifies a particular sample
if (!is.null(SECTION_FILTER)) {
  trials_with_effect_vars <- trials_with_effect_vars |> filter(section == SECTION_FILTER)
}
```
Sanity check - making sure all participants have at least 16 trials and that we have 83 participants
```{r}
low_trial_count <- trials_with_effect_vars |> distinct(SubjectInfo.subjID,Trials.trialID) |> summarize(n=n(),.by=SubjectInfo.subjID) |> filter(n < 25)
nrow(trials_with_effect_vars |> distinct(SubjectInfo.subjID))
```

```{r}
tidy_model <- function(main_effect){
  table_data <- tidy(main_effect, effects = "fixed") %>%
  mutate(
    #p.value = 2 * (1 - pt(abs(statistic),df)),  # Calculate p-values for lmer - just using default calculated ones
    p.value.condensed = case_when(
      p.value < .001 ~ "<.001", 
      p.value < .01 ~ "<.01",
      p.value < .05 ~ "<.05",
      TRUE ~ sprintf("%.3f", p.value)),
    term = case_when(
      term == "(Intercept)" ~ "Intercept",
      term == "scale(age_in_months)" ~ "Age (scaled)",
      #term == "scale(image_similarity)" ~ "Target-distractor image embedding similarity (scaled)",
      TRUE ~ term
    )
  ) %>%
  rename(
    Predictor = term,
    "b" = estimate,
    "SE" = std.error,
    "t" = statistic,  # Note: changed from z to t for lmer
    "p" = p.value.condensed,
    "p.full" = p.value
  ) %>%
  mutate(across(c("b", "SE", "t"), ~round(., 2)))
  return(table_data)
}
```

# Main mixed-effects models
## Model 1 and 2: These are the models we said we'd run in our pre-reg
```{r}
prereg_text_effect <- lmer(scale(corrected_target_looking) ~ scale(text_similarity) + scale(age_in_months) + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (scale(text_similarity) | SubjectInfo.subjID)  
                    + (1|Trials.targetImage)
                    + (1|Trials.imagePair), 
                    data = trials_with_effect_vars)

summary(prereg_text_effect)

#Swapping text similarity with image similarity:
prereg_image_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity) * scale(age_in_months) + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (scale(image_similarity) | SubjectInfo.subjID)  
                    + (1|Trials.targetImage)
                    + + (1|Trials.imagePair), 
                    data = trials_with_effect_vars)
summary(prereg_image_effect)
```
## Models from 1st prereg
```{r}
text_similarity_effect <- lmer(scale(corrected_target_looking) ~ scale(text_similarity) * scale(age_in_months) +
                    + (scale(text_similarity) | SubjectInfo.subjID) 
                    
                    + (1 | Trials.imagePair)
                    + (1 | Trials.targetImage), 
                    data = trials_with_effect_vars)
image_similarity_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity) * scale(age_in_months) +
                    + (scale(image_similarity) | SubjectInfo.subjID) 
                    
                    + (1 | Trials.imagePair)
                    + (1 | Trials.targetImage), 
                    data = trials_with_effect_vars)
summary(text_similarity_effect)
summary(image_similarity_effect)
```

What about this similarity effect per section?
```{r}
image_similarity_effect_sample1 <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*scale(age_in_months)
                     + (1 | SubjectInfo.subjID)
                     + (1|Trials.targetImage), 
                    data = trials_with_effect_vars |> filter(section=="sample1"))
summary(image_similarity_effect_sample1)

image_similarity_effect_sample2 <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*scale(age_in_months)
                     + (1 | SubjectInfo.subjID)
                     + (1|Trials.targetImage), 
                    data = trials_with_effect_vars |> filter(section=="sample2"))
summary(image_similarity_effect_sample2)
```


## BV-image model
Trying out image only models
```{r}
bv_image_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity_bv) * scale(age_in_months) + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                     + (scale(image_similarity_bv) | SubjectInfo.subjID) 
                    + (1|Trials.imagePair)
                    + (1|Trials.targetImage), 
                    data = trials_with_effect_vars)
dinov3_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity_dinov3) * scale(age_in_months) 
                      + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (1 | SubjectInfo.subjID) 
                    
                    + (1|Trials.imagePair)
                    + (1|Trials.targetImage), 
                    data = trials_with_effect_vars)
summary(bv_image_effect)
summary(dinov3_effect)

r.squaredGLMM(prereg_image_effect)
r.squaredGLMM(prereg_text_effect)
r.squaredGLMM(bv_image_effect)
```
Image similarity is trending towards significance.



Checking if text similarity and image similarity are differently correlated with AoA
```{r}
trials_with_effect_vars_metadata <- trials_with_effect_vars |> distinct(Trials.imagePair, text_similarity, image_similarity, image_similarity_bv)
cor.test(trial_metadata$AoA_Est_target, trial_metadata$text_similarity)
cor.test(trial_metadata$AoA_Est_target, trial_metadata$image_similarity)
cor.test(trials_with_effect_vars_metadata$image_similarity, trials_with_effect_vars_metadata$image_similarity_bv)
cor.test(trials_with_effect_vars_metadata$text_similarity, trials_with_effect_vars_metadata$image_similarity_bv)
cor.test(trial_metadata$MeanSaliencyDiff, trial_metadata$image_similarity, method="pearson")
```
Well image similarity has a higher r but both are still insignificant.

## visual saliency without AoA
```{r}
vs_image_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*scale(age_in_months)
                    + scale(MeanSaliencyDiff)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    + (1|Trials.imagePair)
                    , 
                    data = trials_with_effect_vars)

vs_text_effect <- lmer(scale(corrected_target_looking) ~ scale(text_similarity)*scale(age_in_months)
                    + scale(MeanSaliencyDiff)
                    + (scale(text_similarity) | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    + (1|Trials.imagePair)
                    , 
                    data = trials_with_effect_vars)
summary(vs_image_effect)
summary(vs_text_effect)
```
Just a sanity check that adding our saliency metric as a covariate does not affect our similarity effects.


# Alternate window analyses

## Only using first instance of an item
```{r}
first_instance_target <- trials_with_effect_vars |>
  group_by(SubjectInfo.subjID, Trials.targetImage) |>
  arrange(Trials.ordinal, .by_group = TRUE) |>
  slice(1) |>
  ungroup()

second_instance_target <- trials_with_effect_vars |>
  group_by(SubjectInfo.subjID, Trials.targetImage) |>
  arrange(Trials.ordinal, .by_group = TRUE) |>
  slice(2) |>
  ungroup()

primary_targets <- trials_with_effect_vars |>
  filter(Trials.trialType %in% c("easy", "hard"))
  
first_instance_primary_target <- first_instance_target |>
  filter(Trials.trialType %in% c("easy", "hard"))
  
first_instance_image_pair <- trials_with_effect_vars |>
  group_by(SubjectInfo.subjID, Trials.imagePair) |>
  arrange(Trials.ordinal, .by_group = TRUE) |>
  slice(1) |>
  ungroup()


first_instance_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*scale(age_in_months)
                    + scale(MeanSaliencyDiff)
                    + (1 | Trials.ordinal)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    , 
                    data = first_instance_target)

second_instance_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*scale(age_in_months)
                    + scale(MeanSaliencyDiff)
                    + (1 | Trials.ordinal)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    , 
                    data = second_instance_target)

first_instance_pt_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*scale(age_in_months)
                    + scale(MeanSaliencyDiff)
                    + (1 | Trials.ordinal)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    , 
                    data = first_instance_primary_target)

pt_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity) + scale(age_in_months)
                    + scale(MeanSaliencyDiff)
                    + (1 | Trials.ordinal)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    , 
                    data = primary_targets)

first_instance_image_pair_effect <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*scale(age_in_months)
                    + scale(MeanSaliencyDiff)
                    + (1 | Trials.ordinal)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    , 
                    data = first_instance_image_pair)

summary(first_instance_effect)
summary(second_instance_effect)
summary(first_instance_pt_effect)
summary(pt_effect)
summary(first_instance_image_pair_effect)
```
## Random order effects
```{r}
main_image_effect_ordinal <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*scale(age_in_months)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (1 | Trials.ordinal)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    , 
                    data = trials_with_effect_vars)
summary(main_image_effect_ordinal)
```
Order does not explain much variance.

## Target image order effects
```{r}
ranked_trials <- trials_with_effect_vars |>
  group_by(SubjectInfo.subjID, Trials.targetImage) |>
  arrange(Trials.ordinal, .by_group = TRUE) |>
  mutate(
    slice_num = row_number(),
    order = case_when(
      slice_num == 1 ~ -0.5,
      slice_num == 2 ~ 0.5,
      TRUE ~ NA
    )
  )
main_image_effect_ranked <- lmer(scale(corrected_target_looking) ~ scale(image_similarity)*(scale(order))
                                 
                    + scale(AoA_Est_target)
                    + scale(age_in_months)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    , 
                    data = ranked_trials)
# |> filter(Trials.trialType %in% c("easy", "hard")
summary(main_image_effect_ranked)
```

## Z-scoring embeddings
Z-scoring embeddings led to significant image similarity even with AoA as a covariate in section 1 -- todo to include section 2!
```{r}
#main_image_effect_zscored <- lmer(scale(corrected_target_looking) ~ scale(image_sim_zscore)*scale(age_in_months)
#                    + scale(AoA_Est_target)
#                    + scale(MeanSaliencyDiff)
#                    + (1 | SubjectInfo.subjID) 
#                    + (1|Trials.targetImage)
#                    + ( 1 | section), 
#                    data = trials_with_effect_vars)
#summary(main_image_effect_zscored)
```
## Baseline window as a covariate
```{r}
baseline_covariate_looking_text <- lmer(scale(mean_target_looking_critical_window) ~ scale(age_in_months)*scale(text_similarity)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + scale(mean_target_looking_baseline_window)
                    + (scale(text_similarity) || SubjectInfo.subjID) 
                    
                    + (1|Trials.imagePair)
                    + (1|Trials.targetImage), 
                    data = trials_with_effect_vars)

baseline_covariate_looking_image <- lmer(scale(mean_target_looking_critical_window) ~ scale(age_in_months)*scale(image_similarity)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + scale(mean_target_looking_baseline_window)
                    + (scale(image_similarity) || SubjectInfo.subjID) 
                    
                     + (1|Trials.imagePair)
                    + (1|Trials.targetImage), 
                    data = trials_with_effect_vars)

summary(baseline_covariate_looking_text)
summary(baseline_covariate_looking_image)
```
We're seeing some interesting effects. although these models are still singular fits. 

## Predicting critical window looking
```{r}
critical_looking_text <- lmer(scale(mean_target_looking_critical_window) ~ scale(age_in_months)
                    + scale(text_similarity)
                    + scale(image_similarity)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (scale(text_similarity) | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    + (1|Trials.imagePair)
                    , 
                    data = trials_with_effect_vars)

critical_looking_image <- lmer(scale(mean_target_looking_critical_window) ~ scale(age_in_months)*scale(image_similarity)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (scale(image_similarity) | SubjectInfo.subjID) 
                    
                     + (1|Trials.imagePair)
                    + (1|Trials.targetImage), 
                    data = trials_with_effect_vars)

critical_looking_bvimage <- lmer(scale(mean_target_looking_critical_window) ~ scale(age_in_months)*scale(image_similarity_bv)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (scale(image_similarity) | SubjectInfo.subjID) 
                    
                     + (1|Trials.imagePair)
                    + (1|Trials.targetImage), 
                    data = trials_with_effect_vars)

summary(critical_looking_text)
summary(critical_looking_image)
summary(critical_looking_bvimage)
r.squaredGLMM(critical_looking_image)
r.squaredGLMM(critical_looking_text)
```
Similar predictions to our original model.

## Adding window type as a covariate
```{r}
trials_window_type_separated <- trials_with_effect_vars |>
  pivot_longer(cols=c(mean_target_looking_critical_window, mean_target_looking_baseline_window), names_to="window_type", values_to="target_looking") |>
  mutate(window_type = str_replace(window_type, "mean_target_looking_", "")) |>
  mutate(trial_window_c = case_when(
    window_type=="critical_window" ~ 0.5,
    window_type=="baseline_window" ~ -0.5))

window_type_looking_text <- lmer(scale(target_looking) ~ scale(age_in_months)*trial_window_c*scale(text_similarity)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (scale(text_similarity) | SubjectInfo.subjID) 
                    + (1|Trials.imagePair)
                    + (1|Trials.targetImage) , 
                    data = trials_window_type_separated)

window_type_looking_image <- lmer(scale(target_looking) ~ scale(age_in_months)*trial_window_c*scale(image_similarity)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (scale(image_similarity) | SubjectInfo.subjID) 
                    + (1 | Trials.imagePair)
                    + (1|Trials.targetImage) , 
                    data = trials_window_type_separated)

summary(window_type_looking_image)
summary(window_type_looking_text)
```

The interaction makes sense, plotting the predictions here to try to understand what's going on
```{r}
trials_window_type_separated$predicted <- predict(window_type_looking_image)

# Plot interaction effect
ggplot(trials_window_type_separated, aes(x = image_similarity, y = predicted, color = factor(window_type))) +
  geom_point(alpha = 0.5) +   # Add points for raw data
  geom_smooth(method = "lm", se = TRUE) +  # Add regression lines
  labs(title = "Interaction Between Trial Window & Image Similarity",
       x = "Scaled Image Similarity",
       y = "Predicted Target Looking",
       color = "Trial Window") +
  theme_minimal()
```

This is also making me wonder whether we see any signal in how infants look at images in the baseline window.
## Baseline window looking
```{r}
baseline_looking_image <- lmer(scale(mean_target_looking_baseline_window) ~ scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (1 | SubjectInfo.subjID)  + (1 | Trials.targetImage), 
                    data = trials_with_effect_vars)
summary(baseline_looking_image)
```
Can't get this to not be not singular but still fun to see that saliency is predictive.

## Using a shorter critical window
```{r}
short_image_effect <- lmer(scale(corrected_target_looking_short) ~ scale(image_similarity)*scale(age_in_months)
                    + scale(AoA_Est_target)
                    + scale(MeanSaliencyDiff)
                    + (1 | SubjectInfo.subjID) 
                    + (1|Trials.targetImage)
                    , 
                    data = trials_with_effect_vars)

short_text_effect <- lmer(scale(corrected_target_looking_short) ~ scale(text_similarity)*scale(age_in_months)
                    + scale(AoA_Est_target)
                    + (1 | SubjectInfo.subjID)
                    + (1 | Trials.targetImage)
                    , 
                    data = trials_with_effect_vars)
summary(short_text_effect)
summary(short_image_effect)
```
Our effects are not significant with the shorter window.


